Proof equivalence in MLL is PSPACE-complete

### 2015-02-01 main/LMCS.tex
intro para

@@

It should be noted that the above characterisation of  empires relies on the restriction of jumps to target $\1$-formulae only. Otherwise, the first case of the definition should be specialised so that propagation does not traverse jumps into $v$.

>>>>

The result that a canonical representation of multiplicative linear logic is essentially unfeasible raises the question, whether to turn to alternative notions of identity of proofs than that given by $*$-autonomous categories. The literature offers several interesting directions, including but not limited to \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`s's semantically appealing tensorial logic and dialogue categories \cite{Mellies-2012}.

@@

\noindent
It should be noted that the above characterisation of  empires relies on the restriction that we have imposed, that jumps target $\1$-formulae only. Otherwise, the first case of the definition should be specialised so that propagation does not traverse jumps into $v$.
